Data Analysis

### 2023-07-19 ms1_data_analysis.Rmd
Models for LRR

test.df <- data.frame()
for (st in unique(all.pairs_max_accuracy$fsite)){
  for (cp in unique(all.pairs_max_accuracy$comp)){

@@

test.df <- test.df %>%
  mutate(label = ifelse(test.res < 0.05, "*"," "))

@@

siteSLA <- data.woody.brut %>%
  filter(treatment %in% c('i','c','p','h', 'f')) %>%
  mutate(tot_bio = ifelse(is.infinite(tot_bio), NA, tot_bio),
         sla.d.m2kg1 = ifelse(is.infinite(sla.d.m2kg1), NA, sla.d.m2kg1)) %>%
  group_by(site, garden, treatment) %>%
  summarise(cwm.sla = cwmFun(sla.d.m2kg1, n.tot_bio),
            sp.rich = n(),
            total.bio = sum(n.tot_bio))

@@

# Plot of CWM vs species richness
require(scales)
p1 <- ggplot(siteSLAdf, aes(x = sp.rich, y = cwm.sla))+
  geom_point(aes(size = total.bio, color = treatment)) + 
  stat_smooth(method = "lm")+
  scale_x_continuous(trans = 'log2',
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  scale_y_continuous(trans = 'log2',
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +  theme_minimal()

@@

ggpubr::ggarrange(p1,p2, p3)

>>>>

test.df <- data.frame()

all.pairs_max_accuracy$fsite <- factor(all.pairs_max_accuracy$fsite, levels = c("Wanang",
                                                  "Numba","Yawan"))

for (st in unique(all.pairs_max_accuracy$fsite)){
  for (cp in unique(all.pairs_max_accuracy$comp)){

@@

test.df <- test.df %>%
  mutate(label = ifelse(test.res < 0.05, "*"," "))
test.df$fsite <- factor(test.df$fsite, levels = c("Wanang",
                                                  "Numba",
                                                  "Yawan"))

@@

siteSLA <- data.woody.brut %>%
  filter(treatment %in% c('i','c','p','h', 'f')) %>%
  mutate(tot_bio = ifelse(is.infinite(tot_bio), NA, tot_bio),
         sla.d.m2kg1 = ifelse(is.infinite(sla.d.m2kg1), NA, sla.d.m2kg1),
         water.cont = ifelse(is.infinite(water.cont), NA, water.cont)) %>%
  group_by(site, garden, treatment) %>%
  summarise(cwm.sla = cwmFun(sla.d.m2kg1, n.tot_bio),
            cwm.wc = cwmFun(water.cont, n.tot_bio),
            sp.rich = n(),
            total.bio = sum(n.tot_bio))

@@

# Plot of CWM vs species richness
require(scales)

p1.wc <- ggplot(siteSLAdf, aes(x = sp.rich, y = cwm.wc))+
  geom_point(aes(size = total.bio, color = treatment)) + 
  stat_smooth(method = "lm")+
  scale_x_continuous(trans = 'log2',
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  scale_y_continuous(trans = 'log2',
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +  theme_minimal()

p1 <- ggplot(siteSLAdf, aes(x = sp.rich, y = cwm.sla))+
  geom_point(aes(size = total.bio, color = treatment)) + 
  stat_smooth(method = "lm")+
  scale_x_continuous(trans = 'log2',
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  scale_y_continuous(trans = 'log2',
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +  theme_minimal()

@@

# ggpubr::ggarrange(p1,p2, p3)
ggpubr::ggarrange(p1,p1.wc)
